# Data Preprocessing of KUKY 1.0 {#chapter:first-preprocessing}

## KUKY JSON structure

KUKY comes as a JSON file with three top objects:

-   documents

-   labels

-   annotations.

I extract `annotations` and `documents`. Documents contain document
metadata and document texts.Annotations contain labels, document IDs,
and offsets. There are two types of annotation: `Stoplight` and `ArgM`.

## Documents annotated by several annotators

This data set keeps multiple annotations performed for IAA checks.

> ***CAUTION*** De-duplicate the data by annotation `owner` before
> machine learning; that is, do not combine annotations of several
> owners within one document, because the annotations differ not only by
> labels but also by offsets!

```{r message=FALSE}
library(tidyverse, warn.conflicts = FALSE, quietly = TRUE)
library(magrittr, warn.conflicts = FALSE, quietly = TRUE)
library(jsonlite, warn.conflicts = FALSE, quietly = TRUE)
wdpath <- "C:/Users/cinkova/kuky-explore01/kuky_report_bookdown/"
# working directory
kukypath <- "C:/Users/cinkova/kuky-explore01/kuky_report_bookdown/kuky_data/argumentative.json"
# location of the original corpus file
datafolderpath <- "C:/Users/cinkova/kuky-explore01/kuky_report_bookdown/kuky_data/"
# location of the folder containing the corpus 
# - other data objects will go here as well
setwd(wdpath)
kuky <- read_json(kukypath, simplifyVector = FALSE)
docs <- kuky[[1]] %>% 
  purrr::map_df(bind_rows) %>%
  mutate(across(where(is.list), unlist))
#docs converted to a tibble 
if (!exists("annots")  &  file.exists(str_c(datafolderpath, "argumentativeSpanTextsMetadata.rds", sep = "/"))) {
annots <- read_rds("kuky_data/argumentativeSpanTextsMetadata.rds")
} else if (!exists("annots") & !file.exists(str_c(datafolderpath, "argumentativeSpanTextsMetadata.rds", sep = "/"))) {
  stop ("Please run this script from the start to obtain the 'annots' object.")
} else {

annots <- kuky[[3]] %>% 
  map(enframe) %>%
  # could not bind rows just so, 
  # probably due to non-empty list columns "linked_rules", "linked_conclusions" 
  map(pivot_wider) %>% 
  # enframe returned a df with 2 columns: name and value
  # df had to be transformed 
  bind_rows()
# df still considers each column a list
annots %<>% distinct()
write_rds(annots, "kuky_data/ArgM_spans_nested_links.rds")
annots %<>% 
  mutate(across(c("doc_id", "doc_name", 
                  "task_type", "label", "start", "end", 
                  "span_id", "type", "owner"), ~ unlist(.x))) 
#%>% 
  # columns unlisted to vectors, except "linked_rules/conclusions", 
  # which remained lists of vectors. 
  # Mind to keep empty elements if you ever tidyr::unnest_longer them. 
annots %<>%  left_join(docs, by = c("doc_id", "doc_name"))
# doc metadata and document texts added
annots %<>% mutate(span_text = str_sub(plainText, start=start, end=end))

# added span texts by extraction from the documents using the offsets.
saveRDS(annots, file = "kuky_data/argumentativeSpanTextsMetadata.rds")
write_tsv(annots, file = "kuky_data/argumentativeSpanTextsMetadata.tsv")
}
```

```{r}
# check that all spans contain text, must return zero
annots %>% 
  filter(nchar(span_text) == 0 | is.na(span_text)| is.null(span_text)) %>% 
  nrow()
```

## Links between segments

Both annotations are labeled spans with character offsets. In addition,
`ArgM` also contains links between spans. The purpose is to model with
which Rules and which Narratives support which Conclusions. One would
expect links from Rules and Narratives to Conclusions, but the manual
annotation was more ergonomic with linking "Narratives" to their
corresponding "Rules" and "Conclusions". Also "Legal Questions" link to
"Conclusions" \@ref(fig:kukylinks). The links between "Rules" and
"Conclusions" are thus only implicit. Here I will insert the links
between Rules and Conclusions to make them explicit.

![Links in the ArgM
annotation](images/kukydoc.svg){#fig:kukylinks
.illustration}

```{r}
if (!exists("annots")  &  file.exists(str_c(datafolderpath, "argumentativeSpanTextsMetadata.rds", sep = "/"))) {
annots <- read_rds("kuky_data/argumentativeSpanTextsMetadata.rds")
} else if (!exists("annots") & !file.exists(str_c(datafolderpath, "argumentativeSpanTextsMetadata.rds", sep = "/"))) {
  stop ("Please run this script from the start to obtain the 'annots' object.")
} else {
annots_unnested_links <- annots %>% 
  unnest_longer(linked_conclusions, keep_empty = TRUE) %>%
  unnest_longer(linked_rules, keep_empty = TRUE)
}
# The "linked_" columns were nested lists of vectors. 
# Now vectors with more than one element of one type unnested to rows 
# and spans without links were preserved, too.
# But mind that one row can still represent two links, each to a different label.
# I will resolve this later with pivoting the tibble longer. 
```

```{r}
stoplight <- annots_unnested_links %>% filter(task_type == "Stoplight")
# store stoplight annotation that has no links by definition
```

```{r}
argm <- annots_unnested_links %>% filter(task_type == "ArgM")
duplargm <- argm %>% count(span_id, sort = TRUE) # deduplicated span_IDs
# If a Narrative or Legal Question span is linked to e.g. 5 Rules and one Conclusion, it is
# going to produce five rows in this table. So the number of rows in this table is the total number of annotated ArgM. 
# argm %>% filter(span_id == duplargm$span_id[1])
# store argm annotation for further processing
write_rds(duplargm, "kuky_data/frequency_list_of_argmspans.rds")
write_rds(argm, "kuky_data/argm.rds")
```

```{r}
argm_labels <- distinct(argm, label) %>% pull()
argm_labels # the actual Czech span labels
```

```{r}
names(annots_unnested_links)
```

```{r}
argm_labels[c(1, 2, 6)] # I need these to remain correctly encoded
```

```{r}
long_argm <- argm %>% 
  pivot_longer(cols = starts_with("linked"), 
               names_to = "link_type", 
               values_to = "linked_span_id"
              ) %>% 
  mutate(linked_label = case_when(
    link_type == "linked_rules" ~ argm_labels[6], 
    link_type == "linked_conclusions" ~ argm_labels[1],
    link_type == "linked_legal_questions" ~ argm_labels[3],
    link_type == "linked_narratives" ~ argm_labels[2]
    )) %>% distinct()
# Long data frame with each row representing one link 
# (each link type on a separate row, as envisaged above). 
# Most links are empty. 
```

```{r}
explicit_links <- long_argm %>% filter(!is.na(linked_span_id)) %>% 
  filter(label != linked_label) %>% 
  distinct()
# deduplicated long_argm without empty links

```

```{r}
# deduplicated long_argm, only rows with empty links
unlinked_long_argm <- long_argm %>% filter(is.na(linked_span_id)) %>% 
  filter(label != linked_label) %>% distinct(span_id, owner, .keep_all = TRUE)
# These are rows to be added back later. 
# NB: Rules are all empty because they are only referenced by others.
# I will insert their implicit links to Conclusions and add them to linked_argm.
# All rules that acquire links will be removed from here. 
# Only Rules that were not referenced in any other span are going to stay. 
```

```{r}
# adding info about the linked spans (most important: span text!)
linked_argm <- explicit_links %>% 
  right_join(long_argm, 
             by = c("doc_id" = "doc_id", 
                    "owner" = "owner",
                    "linked_span_id" = "span_id",
                    "linked_label" = "label", 
                    "link_type" = "link_type"
                    ), keep = TRUE
             ) %>% 
  #select(!c(linked_label.y,linked_span_id.y, link_type.y)) %>% 
  # linked_span.id.y etc. can create duplicities. Example: x is a Legal Question
  # linked to a Conclusion, which in turn is linked to two different Narratives. 
  # The Narratives are irrelevant here, and therefore we need just one 
  # row representing the link between the Legal Question and Narrative. 
  # This issue is real, although it was rare (10 cases of max 3 repeated values)
  filter(label.x != linked_label.x) %>% 
  filter(link_type.x == link_type.y) %>%
  distinct()

```

```{r}
linked_argm %>% count(link_type.y)
```

```{r}
names(linked_argm)
```

I will create a table of linked rules separately and reverse the order
of columns so that the links go from Rules to Conclusions and
Narratives.

```{r}
linked_rules <- linked_argm  %>% 
  filter(linked_label.x == argm_labels[6])
x2y_cols_linked_rules <- linked_rules %>% select(ends_with(".x")) %>%
  rename_with(., .fn = ~ str_replace(.x, "\\.x", ".y"))
y2x_cols_linked_rules <- linked_rules %>% select(ends_with(".y")) %>%
  rename_with(., .fn = ~ str_replace(.x, "\\.y", ".x"))
linked_rules <- bind_cols(y2x_cols_linked_rules, x2y_cols_linked_rules) 

```

```{r}
#check, should return zero
(names(linked_rules) != names(linked_argm)) %>% sum()  # this returns zero as it should
#but the values in the columns about linking are partly nonsensical
```

```{r}
#the final linked_rules table
linked_rules %<>% 
  mutate(linked_label.x = label.y,
         linked_span_id.x = span_id.y, 
         link_type.x = 
           case_when(label.y == argm_labels[1] ~ "linked_conclusions",
                     label.y == argm_labels[2] ~  "linked_narratives",
                     label.y == argm_labels[3] ~ "linked_legal_questions"
                         ))

```

```{r}
# adding linked_rules to linked argm: new variable linked_argm_incl_rules
linked_argm_incl_rules <- bind_rows(linked_rules, linked_argm)
```

The variable `linked_argm_incl_rules` contains all links I harvested
either directly or by inverting the links to Rules, thereby showing the
rules.

```{r}
#cleanse unlinked_long_argm from the actually linked rules
linked_spans_ids <- linked_argm_incl_rules$span_id.x 
unlinked_long_argm %<>% 
  filter(!(span_id %in% linked_spans_ids)) 
```

Here I have cleaned the table of unlinked spans from spans that had
links (Rules that had been referred to from conclusions or legal
questions).

## Sanity check:

```{r}
linked_distinct_without_rules <- linked_argm %>% distinct(span_id.x) %>% pull()
unlinked_distinct <- unlinked_long_argm %>% distinct(span_id) %>% pull()
linked_rules_distinct <- linked_rules %>% distinct(span_id.x) %>% pull()
total_spans <- length(linked_distinct_without_rules) + 
  length(unlinked_distinct) +
  length(linked_rules_distinct)
```

There are `r nrow(duplargm)` ArgM spans. Thereof are
`r length(unlinked_distinct)` unlinked spans (cleared of Rules that are
actually linked but invisible because they are always just
`linked_span_id` and never in the `span_id` due to the annotation
scheme). Then there are two tables with linked spans. When I deduplicate
their `span_id`s, I get `r length(linked_rules_distinct)` spans with the
Rule spans made visible and `r length(linked_distinct_without_rules)`
spans labeled as Narratives, Legal Questions, or Conclusions. They
indeed total to `r total_spans`.

## Produce datasets

I am going to produce RDS objects and `.tsv` files with both annotations
(Stoplight and ArgM). The code below is mostly renaming columns in the
two ArgM subsets (linked spans vs. unlinked spans)

```{r results='hide'}
names(unlinked_long_argm)
```

```{r}
names(linked_argm_incl_rules)
```

```{r}
var_to_delete <- c("linked_label.y", "linked_span_id.y", "linked_span_id.y", 
                   "link_type.y", "Anonymized.y", "RecipientIndividuation.y", 
                   "RecipientType.y", "AuthorType.y", "Bindingness.y", 
                   "Objectivity.y", "LegalActType.y", "ParentDocumentID.y", 
                   "DocumentVersion.y", "SyllogismBased.y", "Readability.y", 
                   "plainText.y", "note.y", "owner.y", "type.y", "label.y", 
                   "task_type.y", "doc_name.y", "doc_id.y", "span_id.y"
                   )
linked_argm_incl_rules %<>% 
  select(!any_of(var_to_delete)) %>% 
    rename_with(.fn = ~ str_remove(.x, "\\.x")) %>% 
  rename_with(.fn = ~ str_replace(.x, 
                                   "(start|end|span_text)(\\.y)", 
                                   "linked_span_\\1")) %>% 
  rename_with(.fn = ~ str_replace(.x, "_span_span", "_span")) 
```

```{r}
unlinked_long_argm  %<>% mutate(across(c(link_type, linked_label), ~ NA))
```

```{r}
kuky_argm_with_all_links_restored <- linked_argm_incl_rules %>% bind_rows(unlinked_long_argm)
write_rds(kuky_argm_with_all_links_restored, "kuky_data/kuky_argm_with_all_links_restored.rds")
write_tsv(kuky_argm_with_all_links_restored, "kuky_data/kuky_argm_with_all_links_restored.tsv")
write_rds(stoplight, "kuky_data/kuky_stoplight.rds")
write_tsv(stoplight, "kuky_data/kuky_stoplight.tsv")
```
