# Network processing
I have created one full table of annotated ArgM spans (table `argumentativeSpanTextsMetadata` as `.rds` or `.tsv` ) and a table of spans with explicit links (drawn by annotators), which I enhanced with automatic links between Rules and Conclusions `kuky_argm_with_all_links_restored` (`.rds` or `.tsv`).
I want to use this table in the future to generate a list of nodes and a list of edges in a network graph. 
At this point, I will not care about the graph orientation. This means that I will not assume that the columns describing spans to the left (henceforth *source spans*) cover all spans listed in `argumentativeSpanTextsMetadata` and accept that a span can only occur to the right (as a *target span*).
I will also neglect duplicate relations.
Some source spans are that occur on one row as not having a link as well as on other row(s) due to my reconstruction of implicit links. At this point I will not clean the data, but, instead, I will directly create the nodes and edges tables. Duplicities of nodes are going to disappear automatically. 

Regarding duplicate edges (different directions), I believe that it is easier to do this with `igraph` and then export the igraph objects back to data frames.  

```{r}
library(tidyverse, warn.conflicts = FALSE, quietly = TRUE)
library(magrittr, warn.conflicts = FALSE, quietly = TRUE)
library(igraph, warn.conflicts = FALSE, quietly = TRUE)
newdata <- read_rds("kuky_data/kuky_argm_with_all_links_restored.rds")
colnames(newdata)

```
```{r}
argm_labels <- unique(newdata$label) 
# mind that they are ordered differently 
# than in the equally named object in the previous chapter!
argm_labels
```

```{r}
conclusions <- newdata %>% 
  select(doc_id, owner, span_id,span_text,  label, linked_label, linked_span_id, 
          linked_span_text, linked_span_start, linked_span_end) %>% 
  filter(linked_label == argm_labels[2], label == argm_labels[3]) %>% 
  group_by(doc_id, owner, label, linked_label, linked_span_id) %>% 
  add_count(name = "count_separate_parents") %>%
  group_by(doc_id, owner,  linked_label, linked_span_id) %>% 
  add_count(name = "count_total_parents")  %>%
  ungroup()
# for further linking selected only conclusions that are backed by narrations.
```

```{r}
joined_conclusions <- conclusions %>% 
  inner_join(conclusions, by = c("doc_id" = "doc_id", 
                            "owner" = "owner",
                            "linked_label" = "linked_label", 
                            "span_id" = "span_id",
                            "span_text" = "span_text", 
                            #"count_separate_parents" = "count_separate_parents",
                            #"count_total_parents" = "count_total_parents",
                            "label" = "label"
                            ), relationship = "many-to-many") %>% 
  # join tables so that each conclusion meets all conclusions with the same
  # matching Rule, Narrative or Legal Question. 
  filter(linked_span_text.x != linked_span_text.y, 
         linked_span_id.x != linked_span_id.y) %>%
  #removed rows with conclusions pointing to themselves
  rowwise() %>% 
  mutate(minID = min(sort(c(linked_span_id.x, linked_span_id.y))),
         maxID = max(sort(c(linked_span_id.x, linked_span_id.y)))
         ) %>% 
  select(!c(span_id, span_text, label)) %>%
  distinct() %>%
  mutate(joinedID = str_c(minID, maxID, sep = "---")) %>%
  #I'll try something simpler better

  mutate(has_left_fewer_parents = 
           case_when(
             count_total_parents.x > count_total_parents.y ~ "left_greater", 
             count_total_parents.x == count_total_parents.y ~ "left_equal", 
             count_total_parents.x < count_total_parents.y ~ "left_lower")) %>%
ungroup() %>% 
 # filter(has_left_fewer_parents != "left_greater") %>%
  distinct(joinedID, .keep_all = TRUE) 
# originally I wanted to deduplicate the links but then I recalled that 
# the big table (here loaded as newdata) is meant to contain all spans in the 
# left part (span_id etc.). If the links were only one-directional, some spans
# would never appear in the span_id column. When I reconstructed the links 
# between Rules and Conclusions, I created them first with Rules as Sources 
# (left) and Conclusions as targets (right), but then I reconstructed  

```


```{r}
colnames(joined_conclusions)
```
```{r}
joined_conclusions %<>% rename("span_id" = "linked_span_id.x", 
                                      "span_text" = "linked_span_text.x", 
                                      "linked_span_text" = "linked_span_text.y", 
                                      "linked_span_id" = "linked_span_id.y",
                                      "start" = "linked_span_start.x", 
                                      "end" = "linked_span_end.x", 
                                      "linked_span_start" = "linked_span_start.y", 
                                      "linked_span_end" = "linked_span_end.y"
                                      ) %>% 
  select(!c( "minID","maxID", "joinedID", "has_left_fewer_parents", starts_with("count_"))) %>%
  mutate(task_type = "ArgM", label = linked_label)
```

```{r}
colnames(joined_conclusions)
```

```{r}
left_newdata <- newdata %>% select(!c(starts_with("linked")))
colnames(left_newdata)
# these are columns relating to the left (source) span
```

```{r}
newdatacols <- colnames(newdata)  
joined_conclusions %<>% 
  left_join(left_newdata, by = c("doc_id", "task_type", "label", "start", "end", 
                            "span_id", "span_text", "owner"), 
            relationship = "many-to-many") %>% 
  #relocate(all_of(colnames_intersect) ) %>%
  relocate(all_of(newdatacols))
joined_conclusions %<>% mutate(link_type = "between_conclusions") 
```

```{r}
sum(colnames(joined_conclusions) != colnames(newdata)) # sanity check, should be 0
```
```{r}
dupl_spans <- joined_conclusions %>% distinct(span_id) %>% pull()
dupl_linked <- joined_conclusions %>% distinct(linked_span_id) %>% pull()
dupl_all <- c(dupl_spans, dupl_linked) %>% unique()
length(dupl_all)
# these are Conclusion span ids that are connected to other conclusions. 
# Theoretically they 
```

```{r}
# check in joined conclusions whether the source conclusions on the left contain all
# linked conclusions on the right of the table
source_joined_concl <- joined_conclusions %>% distinct(span_id) %>% pull()
target_joined_concl <- joined_conclusions %>% distinct(linked_span_id) %>% pull()
target_alone <- setdiff(target_joined_concl,source_joined_concl)
```


```{r}
joined_conclusions %>% filter(linked_span_id %in% target_alone)
```


```{r}
argm_labels
```











