# Network Analysis {#chapter:network_analysis}

In the previous chapter, I prepared a table of edges for the entire ArgM data. In this chapter, I am going to create the input files for a network graph: a table of nodes and a table of edges. 
I will also create a table of nodes for the stoplight annotation and try and generate edges between ArgM and Stoplight annotation spans using some fuzzy joining based on span offsets. 

I will load these into an [`igraph`](https://r.igraph.org/index.html) object and add network characteristics to the nodes to describe their connectedness. 


```{r message=FALSE, warning=FALSE}
library(tidyverse, warn.conflicts = FALSE, quietly = TRUE)
library(igraph, warn.conflicts = FALSE, quietly = TRUE)
library(tokenizers, warn.conflicts = FALSE, quietly = TRUE)
library(magrittr, warn.conflicts = FALSE, quietly = TRUE)
```

## ArgM data 

```{r}

mydata <- read_rds("kuky_data/kuky_argm_total_links.rds")

colnames(mydata)
```




## Vertices (Nodes)

```{r vertices}
vertices_sourcespans <- mydata %>% select(!starts_with("link")) 
vertices_targetspans <- mydata %>% 
  select(doc_id, doc_name, task_type, label = linked_label, 
         start = linked_span_start, end = linked_span_end, 
         span_id = linked_span_id, type, owner, note, plainText, Readability, 
         SyllogismBased, DocumentVersion, ParentDocumentID, LegalActType, 
         Objectivity, Bindingness, AuthorType, RecipientType, 
         RecipientIndividuation, Anonymized, span_text = linked_span_text) %>% 
  filter(!is.na(span_id))

# Check if column names match
if (!identical(colnames(vertices_sourcespans), colnames(vertices_targetspans))) {
stop("Data frames of vertices of source spans and vertices of target spans must have identical column names!")
}
vertices_df <- bind_rows(vertices_sourcespans, vertices_targetspans) %>%
  select(!c(type, note)) %>%
  relocate(span_id) %>% distinct() 
```

### Sanity check
`vertices_df` must contain the same `span_id`s as span_id in `argm.rds`. 

```{r}
argm_spans <- read_rds("kuky_data/argm.rds") %>% pull(span_id)
vertices_spans <- vertices_df %>% pull(span_id)
base::setdiff(argm_spans, vertices_spans)
base::setdiff(vertices_spans, argm_spans)
rm(argm_spans, vertices_spans)
```


### Additional span features
#### ArgM
- span's relative position in the document 
- span length
- relative span length
- token count in span, neglecting (hopefully most) markup (markdown, html) with a regular expression
- sentence count in span, ditto.

```{r}
argm_vertices_df <- bind_rows(vertices_sourcespans, vertices_targetspans) %>%
  select(!c(type, note)) %>%
  relocate(span_id) %>% distinct()  
# I re-ran this code snippet from above to keep the initialization and further 
# processing of this object in the same code snippet.  
argm_vertices_df %<>% group_by(doc_id, owner) %>% 
  mutate(max_end = max(end)) %>% 
  rowwise() %>% 
  mutate(rel_start = round(start/max_end, 2), 
         rel_end = round(end/max_end, 2),
         span_length = (end - start )
         ) %>% 
  mutate(rel_length = round(span_length/max_end, 4)) %>%
  mutate(across(label, ~ str_replace_all(.x, c("Pravidlo" = "Law", 
                                               "P....h" = "Narrative", 
                                               "Z.v.r" = "Conclusion", 
                                               "Pr.vn...t.zka" = "LegalIssue"
                                               )))) %>% 
  ungroup()    
texts <- argm_vertices_df$span_text %>% 
  str_remove_all("(\\*|#|=|--|\\[(\\d|\\.|\\^)+\\]|\\{[^}]+\\}|[\\\\])")  
  words <-  purrr::map_vec(texts, ~ tokenizers::tokenize_words(.x)) %>% 
    map_int(length)
  sentences <-  purrr::map_vec(texts, ~ tokenizers::tokenize_sentences(.x)) %>% 
    map_int(length)
  
  argm_vertices_df %<>% bind_cols("word_count" = words, "sent_count" = sentences, .name_repair = "unique")
write_rds(argm_vertices_df, "kuky_data/argm_vertices_df.rds")
write_tsv(argm_vertices_df, "kuky_data/argm_vertices_df.tsv")
```


## Edges
The table of edges will have removed rows with no target and de-duplicated links between the same pair of spans (no matter which is target and which is source, since the graph is going to be non-directed).
I will rename the links to encode both ends with English labels (again, their order does not matter)

```{r}
argm_edges_df <- mydata %>% 
  select(c(span_id, linked_span_id, link_type, owner, doc_id, doc_name, label, linked_label)) %>% 
  # later correction: remove unlinked nodes now
  # for correct de-duplication of source nodes (otherwise link_types of Rules get lost)
  filter(!is.na(linked_span_id)) %>%
  rowwise() %>% 
  mutate(across(link_type, ~ str_c(label, linked_label, sep = "-"))) %>%
  mutate(across(link_type, ~ str_replace_all(.x, c("Pravidlo" = "Law", 
                                               "P....h" = "Narrative", 
                                               "Z.v.r" = "Conclusion", 
                                               "Pr.vn...t.zka" = "LegalIssue"
                                               )))) %>% 
  mutate(minspan = min(sort(c(span_id, linked_span_id))),
         maxspan = max(sort(c(span_id, linked_span_id))),
         uid = str_c(minspan, maxspan, sep = "---")
         ) %>% 
  unite(doc_name, owner, sep = "--", col = "docname_owner") %>% 
  ungroup() %>% 
  select(!c(minspan, maxspan)) %>% 
  distinct(uid, .keep_all = TRUE) %>%
  select(!c(uid, label, linked_label))
write_rds(argm_edges_df, "kuky_data/argm_edges_df.rds")
write_tsv(argm_edges_df, "kuky_data/argm_edges_df.tsv")
```
 
Rows before de-duplication: `r nrow(mydata)`.

Rows after de-duplication: `r nrow(argm_edges_df)`. 


## Stoplight data
```{r}
stoplight <- read_rds("kuky_data/kuky_stoplight.rds")
colnames(stoplight)

```
```{r}
stoplight$label %>% unique()
```
```{r}
stoplight <- read_rds("kuky_data/kuky_stoplight.rds") %>%
  mutate(across(label, 
                ~ str_replace_all(.x, c("1_.*" = "Incomprehensible",
                                        "2_.*" = "Superfluous", 
                                        "3_.*" = "Relevant", 
                                        "koment.*" = "Comment"
                                        )))) %>% 
  select(!c(type, starts_with("linked_"), note)) %>% 
  relocate(span_id) %>% distinct() %>%
  group_by(doc_id, owner) %>% 
  mutate(max_end = max(end)) %>% 
  rowwise() %>% 
  mutate(rel_start = round(start/max_end, 2), 
         rel_end = round(end/max_end, 2),
         span_length = (end - start )
         ) %>% 
  mutate(rel_length = round(span_length/max_end, 4))

texts <- stoplight$span_text %>% 
  str_remove_all("(\\*|#|=|--|\\[(\\d|\\.|\\^)+\\]|\\{[^}]+\\}|[\\\\])")  
  words <-  purrr::map_vec(texts, ~ tokenizers::tokenize_words(.x)) %>% 
    map_int(length)
  sentences <-  purrr::map_vec(texts, ~ tokenizers::tokenize_sentences(.x)) %>% 
    map_int(length)
  
stoplight_vertices_df <- stoplight %>% bind_cols("word_count" = words, "sent_count" = sentences, .name_repair = "unique")
write_rds(stoplight_vertices_df, "kuky_data/stoplight_vertices_df.rds")
write_tsv(stoplight_vertices_df, "kuky_data/stoplight_vertices_df.tsv")
  
```


## Combining the Stoplight and ArgM edges
The stoplight annotation does not contain any links, but the spans in ArgM and the spans in Stoplight ought to be linked so that we can see how these two annotations interact. I will join them based on any overlap of span offsets in the given document-owner pair.  


```{r}
# dplyr join, use join_by
# Find every time a segment overlaps a reference in any way.
#by <- join_by(chromosome, overlaps(x$start, x$end, y$start, y$end))
#full_join(segments, reference, by)

by_overlaps <- dplyr::join_by(doc_id, 
                              owner, 
                              doc_name, 
                              overlaps(x$start,
                                      x$end, 
                                      y$start,
                                      y$end))
stoplight_edges_df <- stoplight_vertices_df %>%
  full_join(vertices_df, by = by_overlaps, keep = TRUE) %>% 
  mutate(link_type = "Spotlight_ArgM") %>%
  unite(col = "docname_owner", doc_name.x, owner.x,remove = FALSE ) %>%
  select(c(span_id = span_id.x,
           linked_span_id = span_id.y, 
           link_type,
           owner = owner.x,
           docname_owner,
           doc_id = doc_id.x
           ))
all_edges_df <- bind_rows(argm_edges_df, stoplight_edges_df)



```


```{r}
all_vertices_df <- bind_rows(argm_vertices_df, stoplight_vertices_df)
```
```{r}
write_rds(all_edges_df, "kuky_data/all_edges_df.rds")
write_rds(all_vertices_df, "kuky_data/all_vertices_df.rds")
write_tsv(all_edges_df, "kuky_data/all_edges_df.tsv")
write_tsv(all_vertices_df, "kuky_data/all_vertices_df.tsv")
```






## Creating the `igraph` objects

Each document-owner pair will be represented by its own graph. 
Therefore I will work with a list of vertices and edges data frames. 

```{r}
docs_owners <- all_vertices_df %>% distinct(doc_id, owner) %>%
  unite(col = "doc_owner", doc_id, owner, sep = "--", remove = FALSE) 
listnames <- docs_owners %>% pull(doc_owner) 
# this whole snippet provides names to the elements of the lists of vertices and edges. It encodes the doc_id and the owner id. 
```

```{r}
doc_ids <- docs_owners$doc_id # vector of doc_ids
owner_vec <- docs_owners$owner # vector of owner ids
vertices_list <- doc_ids %>% 
  purrr::map2(.y = owner_vec, 
              .f = ~ filter(all_vertices_df, doc_id == .x, owner == .y))
vertices_list %<>% purrr::set_names(listnames)
# This created a list of vertices_dfs split by doc_id-owner combinations
edges_list <- doc_ids %>%
  purrr::map2(.y = owner_vec,
              .f = ~ filter(all_edges_df, doc_id == .x, owner == .y))
edges_list %<>% purrr::set_names(listnames) %>% 
  purrr::map(~ filter(.x, !is.na(linked_span_id)))
# This created a list of edges_dfs split by doc_id-owner combinations. 
# Igraph does not accept edges with no targets, so I removed them.
write_rds(edges_list, "kuky_data/edges_list.rds")
write_rds(vertices_list, "kuky_data/vertices_list.rds")
```

```{r}
igraphs <- purrr::map2(
  .x = edges_list, 
  .y = vertices_list,
  ~ igraph::graph_from_data_frame(d = .x, vertices = .y, directed = FALSE))
write_rds(igraphs, "kuky_data/igraphs.rds")
```

I would like to display each document in a grid of vertices ordered according to the span start.
First I have to order the vertices according to their offset starts. 
It is very sparsely documented in `igraph`, and therefore I will explain the procedure step by step, based on an explanation by MS Copilot. 

The most naive approach would be this: 

```{r eval=FALSE}
# V(text_graph)$start <- V(text_graph)$start[order(V(text_graph)$start)]
```

When this fails to permute the order of edges, it is intelligible: indeed, manipulating one vertex attribute will not necessarily manipulate the order of the vertices. 
There is a function called `igraph::permute`, and this is supposed to do that properly. It only wants the graph and a numeric vector representing the permutation order. So the first thing one would do is to give it the ordering indices produced by `order()`, like so: 

```{r eval=FALSE}
#perm <- order(V(text_graph)$start)
#permute(text_graph, permute = perm)
```

This will do something, but the result is going to be incorrect!!!!
`perm` says: "My first element is now the one that used to rank 19th. My second element is now the one that used to rank 37th." and so on. But what `permute` needs to hear is: "The original first element belongs on rank 9. The original second element belongs on rank 14". And so on. It is called inverse permutation. And this is how it can be implemented: 


```{r eval=FALSE}

# # Original order of vertices by 'start'
# start_vals <- V(text_graph)$start
# 
# # Get the order of vertex indices by 'start'
# sorted_indices <- order(start_vals)
# 
# # Invert the permutation: new[i] = which(sorted_indices == i)
# perm <- match(seq_along(sorted_indices), sorted_indices) # this is the trick!!!
# 
# # Apply the permutation
# text_graph_sorted <- permute(text_graph, perm)
# 
# # Check the result
# V(text_graph_sorted)$start


```
I want to perform this permutation on all documents simultaneously, so I will write it as a function.  
```{r}
permute_start <- function(text_graph) {
  # this function permutes the vertices of a graph by the values of 
  # the attribute "start" (specific to my data)
  start_vals <- V(text_graph)$start
  sorted_indices <- order(start_vals)
  perm <- match(seq_along(sorted_indices), sorted_indices)
  text_graph_sorted <- permute(text_graph, perm)
  return(text_graph_sorted)
}
```


```{r}
igraphs_sorted <- igraphs %>% map(permute_start)
write_rds(igraphs_sorted, "kuky_data/igraphs_sorted.rds")
```







