# Creating `igraph` objects {#chapter:network_analysis}

In the previous chapter, I prepared a table of edges for the entire ArgM
data, which contains all attributes of all nodes. In this chapter, I am
going to create the input files for a network graph: a table of nodes
and a table of edges. The edge table must not contain node attributes.
Nodes are called vertices in the network processing library `igraph`, so
I will switch the term too.

Originally, I wanted to include the Stoplight annotation as a subset of
vertices, but this just cluttered the resulting graph. Therefore I
decided to just record for each ArgM span which Stoplight annotation it
overlaps with. Most overlapped with just one. There were not even 200
spans that overlapped with Stoplights spans of several different labels.
I recorded the individual proportions of overlaps with the three
Stoplight labels in additional columns. For the modeling purposes,
probably the only interesting column is the Relevant column, where,
again, the proportion is mostly 1.00 anyway. I fully abstract from
Stoplight span IDs and only record which Stoplight labels would occur on
tokens in ArgM spans. This will work only at the level of spans; that
is, I will not know where in the ArgM span the Stoplight labels shift.
This occurs so rarely that modeling it in full detail is not worth the
effort.

In the next chapter, I will load the vertices and edges tables into an
[`igraph`](https://r.igraph.org/index.html) object and add network
characteristics to the nodes to describe their connectedness. Here I
will just add columns that would be too difficult to generate once the
tables have become an `igraph` object.

```{r message=FALSE, warning=FALSE}
library(tidyverse, warn.conflicts = FALSE, quietly = TRUE)
library(igraph, warn.conflicts = FALSE, quietly = TRUE)
library(tokenizers, warn.conflicts = FALSE, quietly = TRUE)
library(magrittr, warn.conflicts = FALSE, quietly = TRUE)
```

## ArgM data

```{r}

mydata <- read_rds("kuky_data/kuky_argm_total_links.rds")

colnames(mydata)
```

## Vertices (Nodes)

```{r vertices}
vertices_sourcespans <- mydata %>% select(!starts_with("link")) 
vertices_targetspans <- mydata %>% 
  select(doc_id, doc_name, task_type, label = linked_label, 
         start = linked_span_start, end = linked_span_end, 
         span_id = linked_span_id, type, owner, note, plainText, Readability, 
         SyllogismBased, DocumentVersion, ParentDocumentID, LegalActType, 
         Objectivity, Bindingness, AuthorType, RecipientType, 
         RecipientIndividuation, Anonymized, span_text = linked_span_text) %>% 
  filter(!is.na(span_id))

# Check if column names match
if (!identical(colnames(vertices_sourcespans), colnames(vertices_targetspans))) {
stop("Data frames of vertices of source spans and vertices of target spans must have identical column names!")
}
vertices_df <- bind_rows(vertices_sourcespans, vertices_targetspans) %>%
  select(!c(type, note)) %>%
  relocate(span_id) %>% distinct() 
```

### Sanity check

`vertices_df` must contain the same `span_id`s as span_id in `argm.rds`.

```{r}
argm_spans <- read_rds("kuky_data/argm.rds") %>% pull(span_id)
vertices_spans <- vertices_df %>% pull(span_id)
base::setdiff(argm_spans, vertices_spans)
base::setdiff(vertices_spans, argm_spans)
rm(argm_spans, vertices_spans)
```

### Additional span features

#### ArgM

-   span's relative position in the document
    <!-- tohle dodelam 16.6.25-->
-   span's position in the document (rank) `spanposition_global`
-   span's position in the document within its label (rank)
    `spanposition_intralabel`
-   `docname_owner` (this is going to be a graph attribute and I will
    use it in plot titles ) <!--konec dodatecnych dodelavek-->
-   span length
-   relative span length
-   token count in span, neglecting (hopefully most) markup (markdown,
    html) with a regular expression
-   sentence count in span, ditto.

```{r}
argm_vertices_df <- bind_rows(vertices_sourcespans, vertices_targetspans) %>%
  select(!c(type, note)) %>%
  relocate(span_id) %>% distinct()  
# I re-ran this code snippet from above to keep the initialization and further 
# processing of this object in the same code snippet.  
argm_vertices_df %<>% group_by(doc_id, owner) %>% 
  mutate(max_end = max(end)) %>% 
  rowwise() %>% 
  mutate(rel_start = round(start/max_end, 4), 
         rel_end = round(end/max_end, 4),
         span_length = (end - start )
         ) %>% 
  mutate(rel_length = round(span_length/max_end, 4)) %>%
  mutate(across(label, ~ str_replace_all(.x, c("Pravidlo" = "Law", 
                                               "P....h" = "Narrative", 
                                               "Z.v.r" = "Conclusion", 
                                               "Pr.vn...t.zka" = "LegalIssue",
                                               "Rada" = "Advice", 
                                               "V.zva" = "Request",
                                               "Koment.*" = "Comment"
                                               )))) %>% 
  group_by(doc_id, owner) %>%
  mutate(span_position_global = rank(start, ties.method = "first")) %>% 
  group_by(doc_id, owner, label) %>%
  mutate(span_position_intralabel = rank(start, ties.method = "first")) %>%
  ungroup() %>%
  mutate(docname_owner = str_c(doc_name, owner, sep = "--"))  %>% 
  rename_with(.cols = c("plainText", "owner", 
                        "docname_owner", "Readability", "SyllogismBased",
                        "DocumentVersion", "ParentDocumentID", "LegalActType",
                        "Objectivity", "Bindingness", "AuthorType", 
                        "RecipientType", "RecipientIndividuation","Anonymized"), 
              .fn = ~ str_c("doc_", .x)) %>% 
  relocate(starts_with("doc_"),.after = everything()) %>% 
  rename_with(.cols = c(!matches("^(doc_|span)")), 
              .fn = ~ str_c("span_", .x))
texts <- argm_vertices_df$span_text %>% 
  str_remove_all("(\\*|#|=|--|\\[(\\d|\\.|\\^)+\\]|\\{[^}]+\\}|[\\\\])")  
  words <-  purrr::map_vec(texts, ~ tokenizers::tokenize_words(.x)) %>% 
    map_int(length)
  sentences <-  purrr::map_vec(texts, ~ tokenizers::tokenize_sentences(.x)) %>% 
    map_int(length)
  
  argm_vertices_df %<>% bind_cols("span_word_count" = words, "span_sent_count" = sentences, .name_repair = "unique")
write_rds(argm_vertices_df, "kuky_data/argm_vertices_df.rds")
write_tsv(argm_vertices_df, "kuky_data/argm_vertices_df.tsv")
```

## Edges

The table of edges will have removed rows with no target and
de-duplicated links between the same pair of spans (no matter which is
target and which is source, since the graph is going to be
non-directed). I will rename the links to encode both ends with English
labels (again, their order does not matter)

```{r}
argm_edges_df <- mydata %>% 
  select(c(span_id, linked_span_id, link_type, owner, doc_id, doc_name, label, linked_label, owner)) %>% 
  # later correction: remove unlinked nodes now
  # for correct de-duplication of source nodes (otherwise link_types of Rules get lost)
  filter(!is.na(linked_span_id)) %>%
  rowwise() %>% 
  mutate(across(link_type, ~ str_c(label, linked_label, sep = "-"))) %>%
  mutate(across(link_type, ~ str_replace_all(.x, c("Pravidlo" = "Law", 
                                               "P....h" = "Narrative", 
                                               "Z.v.r" = "Conclusion", 
                                               "Pr.vn...t.zka" = "LegalIssue"
                                               )))) %>% 
  mutate(minspan = min(sort(c(span_id, linked_span_id))),
         maxspan = max(sort(c(span_id, linked_span_id))),
         uid = str_c(minspan, maxspan, sep = "---")
         ) %>% # 
  #join with vertices and get relative length of span and then of linked_span
  left_join(argm_vertices_df[, c("span_id", "span_rel_length")], by = c("span_id")) %>%
  left_join(argm_vertices_df[, c("span_id", "span_rel_length")], by = c("linked_span_id" = "span_id")) %>%
  rowwise() %>%
  mutate(weight = sum(c_across(starts_with("span_rel_length")))) %>% #
  #join with vertices, get relative starts and ends of span and linked_span 
  left_join(argm_vertices_df[, c("span_id", "span_rel_start", "span_rel_end")], 
            by = c("span_id")) %>% 
  left_join(argm_vertices_df[, c("span_id", "span_rel_start", "span_rel_end")],
            by = c("linked_span_id" = "span_id")) %>%
  # subtract the relative end of the one earlier in text from the relative start of the one later in text. 
  mutate(rel_distance = max(
    c_across(contains("rel_start")) - min(c_across(contains("rel_end"))))) %>% 
  select(!c(contains("span_rel"))) %>% 
  unite(doc_name, owner, sep = "--", col = "docname_owner", remove = FALSE) %>% 
  ungroup() %>%
  select(!c(minspan, maxspan)) %>% 
  distinct(uid, .keep_all = TRUE) %>%
  select(!c(uid, label, linked_label))
write_rds(argm_edges_df, "kuky_data/argm_edges_df_undirected.rds")
write_tsv(argm_edges_df, "kuky_data/argm_edges_df_undirected.tsv")

```



## Stoplight data

```{r}
stoplight <- read_rds("kuky_data/kuky_stoplight.rds")
colnames(stoplight)

```

```{r}
stoplight$label %>% unique()
```

```{r}
stoplight <- read_rds("kuky_data/kuky_stoplight.rds") %>%
  mutate(across(label, 
                ~ str_replace_all(.x, c("1_.*" = "Incomprehensible",
                                        "2_.*" = "Superfluous", 
                                        "3_.*" = "Relevant", 
                                        "koment.*" = "Comment"
                                        )))) %>% 
  select(!c(type, starts_with("linked_"), note)) %>% 
  relocate(span_id) %>% distinct() %>%
  group_by(doc_id, owner) %>% 
  mutate(max_end = max(end)) %>% 
  rowwise() %>% 
  mutate(rel_start = round(start/max_end, 4), 
         rel_end = round(end/max_end, 4),
         span_length = (end - start )
         ) %>% 
  mutate(rel_length = round(span_length/max_end, 4)) %>% 
  ungroup() %>%
  mutate(docname_owner = str_c(doc_name, owner))  %>% 
  rename_with(.cols = c("plainText", "owner", 
                        "docname_owner", "Readability", "SyllogismBased",
                        "DocumentVersion", "ParentDocumentID", "LegalActType",
                        "Objectivity", "Bindingness", "AuthorType", 
                        "RecipientType", "RecipientIndividuation","Anonymized"), 
              .fn = ~ str_c("doc_", .x)) %>% 
  relocate(starts_with("doc_"),.after = everything()) %>% 
  rename_with(.cols = c(!matches("^(doc_|span)")), 
              .fn = ~ str_c("span_", .x))

texts <- stoplight$span_text %>% 
  str_remove_all("(\\*|#|=|--|\\[(\\d|\\.|\\^)+\\]|\\{[^}]+\\}|[\\\\])")  
  words <-  purrr::map_vec(texts, ~ tokenizers::tokenize_words(.x)) %>% 
    map_int(length)
  sentences <-  purrr::map_vec(texts, ~ tokenizers::tokenize_sentences(.x)) %>% 
    map_int(length)
  
stoplight_vertices_df <- stoplight %>% bind_cols("span_word_count" = words, "span_sent_count" = sentences, .name_repair = "unique")
write_rds(stoplight_vertices_df, "kuky_data/stoplight_vertices_df.rds")
write_tsv(stoplight_vertices_df, "kuky_data/stoplight_vertices_df.tsv")
  
```

## Combining the Stoplight and ArgM edges

If needed, the stoplight annotation can be added to ArgM as vertices and
edges. Here I create links between the Stoplight and ArgM annotations by
joining them by any overlap of span offsets in the given document-owner
pair. I also compute for each ArgM span by which proportion of
characters it belongs to which Stoplight label. Most belong to only one
label, fewer than 200 belong to several labels. Note that I consider
labels, not Stoplight spans. I abstract from their IDs. This implies
that when an ArgM span fully belongs to one label, it could in fact be
linked with a sequence of several Stoplight spans with the same label.\
In the same vein, when an ArgM span belongs to two labels, we cannot say
how many Stoplight spans of which label it is linked to.

First I wanted to add the Stoplight annotation to the graphs as
additional nodes and edges, but it would probably clutter the graph. So
I revisited this decision, and instead of adding new nodes and vertices,
I will make the Stoplight annotation attributes of ArgM vertices.

Each Stoplight label is going to be represented by one attribute. The
values are going to be proportions of the given ArgM span that are
marked with the individual Stoplight labels. When `Relevant` is 1.00,
the ArgM span is not linked to other Stoplight labels. In five cases,
the Stoplight annotation contained a`Comment`, which was designed as a
label of the same type as `Relevant`, `Superfluous`, and
`Incomprehensible`. The proportion of the comment was added to
`Relevant`. Combinations of `Comment` with other labels without
`Relevant` never occurred.

```{r}
# dplyr join, use join_by
# Find every time a segment overlaps a reference in any way.
#by <- join_by(chromosome, overlaps(x$start, x$end, y$start, y$end))
#full_join(segments, reference, by)

by_overlaps <- dplyr::join_by(doc_id, 
                              doc_owner, 
                              doc_name, 
                              overlaps(x$span_start,
                                      x$span_end, 
                                      y$span_start,
                                      y$span_end))
stoplight_edges_df <- stoplight_vertices_df %>%
  full_join(argm_vertices_df, by = by_overlaps, keep = TRUE) %>% 
  mutate(link_type = "Stoplight_ArgM") %>%
  unite(col = "docname_owner", doc_name.x, doc_owner.x,remove = FALSE ) %>%
  select(c(span_id = span_id.x,
           linked_span_id = span_id.y, 
           link_type,
           doc_owner = doc_owner.x,
           docname_owner,
           doc_id = doc_id.x, span_start.x, span_end.x, span_start.y, span_end.y, span_label.x, 
           span_word_count.x, span_sent_count.x, span_word_count.y, span_sent_count.y
           ))
all_edges_df <- bind_rows(argm_edges_df, stoplight_edges_df) %>% 
  filter(!is.na(linked_span_id))

```

```{r}
enrichment <- stoplight_edges_df %>% 
  rowwise() %>% 
  mutate(overlap = max(0, min(span_end.x, span_end.y) - max(span_start.x, span_start.y))) %>% 
  ungroup() %>% 
  group_by(linked_span_id, span_label.x) %>% 
  mutate(overlap_samelabel = sum(overlap)) %>% # sum is correct here 
  # to abstract from boundaries between spans with the same stoplight label
  group_by(linked_span_id) %>% 
  mutate(proportion_stoplight_label = overlap_samelabel/sum(overlap)) %>%
  ungroup()  %>% 
  filter(overlap > 1) %>% 
  #filter(proportion_stoplight_label < 1) %>% # there was at least one such because join_by worked with open intervals.
  #select(c(linked_span_id, label.x, overlap, overlap_samelabel, proportion_stoplight_label)) %>%
  group_by(linked_span_id, doc_owner,docname_owner, doc_id, link_type ) %>% 
  nest() %>% 
  unnest_wider(data) %>%
  select(!c(starts_with("start"), starts_with("end"),
            span_id, overlap, overlap_samelabel)) %>%
  mutate(across(c(span_label.x,proportion_stoplight_label), 
                ~ purrr::map(.x, ~unique(.x) ))) %>% 
  ungroup()  %>% unnest_longer(c("span_label.x", "proportion_stoplight_label")) %>% 
  pivot_wider(names_from = "span_label.x", values_from = "proportion_stoplight_label") %>% 
  # get rid of comments. They are encoded as Stoplight spans. 
  # Only five occurred in the data, can be neglected. 
  mutate(across(Relevant, ~ if_else(
    !is.na(.x) & is.na(Superfluous) & is.na(Incomprehensible) & !is.na(Comment), 
    true = .x + Comment, false = .x))) %>% 
  filter(!(is.na(Relevant) & is.na(Superfluous) & is.na(Incomprehensible))) %>%
  select(!c(Comment, link_type, docname_owner))

```

Some ArgM vertices got lost, check which:

```{r}
missing_argm <- setdiff(argm_vertices_df$span_id, enrichment$linked_span_id)

missing_argm_df <- argm_vertices_df %>% filter(span_id %in% missing_argm)
missing_argm_df %>% select(doc_name, span_text, span_label)
```

They are few, belong to only five documents and are not important for
the texts. They are going to have `NA` in the new attributes.\
And I am going to round the proportions to four decimal digits.

```{r}
argm_vertices_enriched_df <- argm_vertices_df %>% 
  left_join(enrichment, by = c("doc_id", 
                               "span_id" = "linked_span_id", 
                               "doc_owner"
                               )) %>%
  mutate(across(c("Relevant", 
                  "Superfluous", 
                  "Incomprehensible"), ~ round(.x, 4))) %>%
  select(c(span_id,
           span_label,
           span_start,
           span_end,
           span_rel_start,
           span_rel_end, 
           span_length,
           span_rel_length, 
           span_position_global, 
           span_position_intralabel, 
           span_word_count, 
           span_sent_count, 
           span_text, 
           span_task_type,
           "span_Relevant" = Relevant,
           "span_Superfluous" = Superfluous, 
           "span_Incomprehensible" = Incomprehensible,
           "metadoc_docname_owner" = doc_docname_owner,
           doc_id,
           doc_name,
           doc_owner, 
           doc_plainText, 
           "metadoc_Readability" = doc_Readability, 
           "metadoc_SyllogismBased" = doc_SyllogismBased, 
           "metadoc_DocumentVersion" = doc_DocumentVersion,
           "metadoc_ParenDocumentID" = doc_ParentDocumentID, 
           "metadoc_LegalActType" = doc_LegalActType,
           "metadoc_Objectivity" = doc_Objectivity, 
           "metadoc_Bindingness" = doc_Bindingness, 
           "metadoc_AuthorType" = doc_AuthorType, 
           "metadoc_RecipientType" = doc_RecipientType,
           "metadoc_RecipientIndividuation" = doc_RecipientIndividuation,
           "metadoc_Anonymized" = "doc_Anonymized")) %>%
  mutate(across(c(span_Relevant, 
                  span_Superfluous, 
                  span_Incomprehensible), 
                ~ replace_na(.x, 0)))


```

```{r}
all_vertices_df <- bind_rows(argm_vertices_df, stoplight_vertices_df) 
```

```{r}
write_rds(stoplight_edges_df, "kuky_data/stoplight_edges_df.rds")
write_tsv(stoplight_edges_df, "kuky_data/stoplight_edges_df.tsv")
write_rds(all_edges_df, "kuky_data/all_edges_df.rds")
write_rds(all_vertices_df, "kuky_data/all_vertices_df.rds")
write_tsv(all_edges_df, "kuky_data/all_edges_df.tsv")
write_tsv(all_vertices_df, "kuky_data/all_vertices_df.tsv")
write_rds(argm_vertices_enriched_df, "kuky_data/argm_vertices_stoplight_enriched_df.rds")
write_tsv(argm_vertices_enriched_df, "kuky_data/argm_vertices_stoplight_enriched_df.tsv")
```

## Redesign of the edges data frame to enable directed graphs
A post-hoc enhancement: Now the first column (source vertex in directed graphs) contains the vertex that appears earlier in the text than its counterpart vertex in the second column (target vertex in directed graphs). I will not save it under a different name since
there is no need to preserve the original one where the order of vertices in the pair was random. 
```{r}
### Revision 2025-06-27 
# I added code from 04_network_preprocessing02. This will make 
vertices_df <- read_rds("kuky_data/argm_vertices_stoplight_enriched_df.rds") %>%
  select(span_id, span_position_global,)
edges_df <- read_rds("kuky_data/argm_edges_df.rds") %>% 
  left_join(vertices_df, by = c("span_id" = "span_id")) %>% 
  rename(first_span_position_global = span_position_global) %>% 
  left_join(vertices_df, by = c("linked_span_id" = "span_id")) %>%
  rename(second_span_position_global = span_position_global)
sources <- edges_df %>% filter(first_span_position_global < second_span_position_global)
targets <- edges_df %>% 
  filter(first_span_position_global > second_span_position_global) %>% 
  rename(span_id_new = linked_span_id, linked_span_id_new = span_id) %>%
  rename_with(~ str_remove(.x, "_new")) %>% 
  relocate(span_id) # the position indices still reflect the original column order
  # no worry, they are to be deleted anyway
edges_df <- bind_rows(sources, targets) %>% select(!c(contains("span_position_global")))
write_rds(edges_df, "kuky_data/argm_edges.rds")
write_tsv(edges_df, "kuky_data/argm_edges.tsv")
```


## Creating the `igraph` objects

Each document-owner pair will be represented by its own graph. Therefore
I will work with a list of vertices and edges data frames.

```{r}
# asi vyhodit
# docs_owners <- argm_vertices_enriched_df %>% distinct(doc_name, doc_owner) %>%
#   unite(col = "doc_owner", doc_name, doc_owner, sep = "--", remove = FALSE)
# #docnames_owners <- argm_vertices_enriched_df$metadoc_docname_owner %>% unique()
# listnames <- docs_owners %>% pull(doc_owner) 
#listnames <- docnames_owners
# this whole snippet provides names to the elements of the lists of vertices and edges. It encodes the doc_id and the owner id. 
```

```{r}
owner_vec <- argm_vertices_enriched_df %>% 
  distinct(metadoc_docname_owner) %>% 
  pull()
listnames <- owner_vec
```

```{r}
vertices_list <- owner_vec %>% 
  purrr::map(.f = ~ filter(argm_vertices_enriched_df, 
                           metadoc_docname_owner == .x))
vertices_list %<>% purrr::set_names(listnames)
# This created a list of vertices_dfs split by doc_id-owner combinations
edges_list <- owner_vec %>%
  purrr::map(.f = ~ filter(argm_edges_df, docname_owner == .x))
edges_list %<>% purrr::set_names(listnames) %>% 
  purrr::map(~ filter(.x, !is.na(linked_span_id)))
# This created a list of edges_dfs split by doc_id-owner combinations. 
# Igraph does not accept edges with no targets, so I removed them.
write_rds(edges_list, "kuky_data/edges_list.rds")
write_rds(vertices_list, "kuky_data/vertices_list.rds")
```

```{r}
# doc_ids <- docs_owners$doc_id # vector of doc_ids
# owner_vec <- docs_owners$doc_owner # vector of owner ids
# vertices_list <- doc_ids %>% 
#   purrr::map2(.y = owner_vec, 
#               .f = ~ filter(argm_vertices_enriched_df, doc_id == .x, doc_owner == .y))
# vertices_list %<>% purrr::set_names(listnames)
# # This created a list of vertices_dfs split by doc_id-owner combinations
# edges_list <- doc_ids %>%
#   purrr::map2(.y = owner_vec,
#               .f = ~ filter(argm_edges_df, doc_id == .x, owner == .y))
# edges_list %<>% purrr::set_names(listnames) %>% 
#   purrr::map(~ filter(.x, !is.na(linked_span_id)))
# # This created a list of edges_dfs split by doc_id-owner combinations. 
# # Igraph does not accept edges with no targets, so I removed them.
# write_rds(edges_list, "kuky_data/edges_list.rds")
# write_rds(vertices_list, "kuky_data/vertices_list.rds")
```

```{r}
igraphs_nondirected <- purrr::map2(
  .x = edges_list, 
  .y = vertices_list,
  ~ igraph::graph_from_data_frame(d = .x, vertices = .y, directed = FALSE))
#write_rds(igraphs, "kuky_data/igraphs_.rds")
```

### A small digression for future visualization

At a point, I may want to display each document in a grid of vertices
ordered according to the span start. I might have to compute the
coordinate positions for each vertex according to its global position
(`span_position_global` in the vertices table) or its offset start
(`span_start` ditto). I believe this to be easier if I make sure the
vertices are properly ordered right from the beginning.
Sorting/arranging vertices (here according to an attribute of their
source vertex) is very sparsely documented in `igraph`, and therefore I
will record the procedure step by step, based on an explanation by MS
Copilot, for my future reference.

The most naive approach would be this and it would fail.

```{r eval=FALSE}
# V(text_graph)$span_start <- V(text_graph)$span_start[order(V(text_graph)$span_start)]
```

The failure of this approach is intelligible: indeed, manipulating one
vertex attribute will not necessarily manipulate the order of the
vertices. To manipulate the order of the entire vertices, `igraph`
offers a function called `igraph::permute`. It only wants the graph and
a numeric vector representing the permutation order. So the first thing
one would do is to give it the ordering indices produced by `order()`,
like so:

```{r eval=FALSE}
#perm <- order(V(text_graph)$span_start)
#permute(text_graph, permute = perm)
```

This will do something, but the result is going to be incorrect!!!!
`perm` says: "My first element is now the one that used to rank 19th. My
second element is now the one that used to rank 37th." and so on. But
what `permute` needs to hear is: "The original first element belongs on
rank 9. The original second element belongs on rank 14". And so on. It
is called inverse permutation. And this is how it can be implemented:

```{r eval=FALSE}

# # Original order of vertices by 'span_start'
# start_vals <- V(text_graph)$span_start
# 
# # Get the order of vertex indices by 'start'
# sorted_indices <- order(start_vals)
# 
# # Invert the permutation: new[i] = which(sorted_indices == i)
# perm <- match(seq_along(sorted_indices), sorted_indices) # this is the trick!!!
# 
# # Apply the permutation
# text_graph_sorted <- permute(text_graph, perm)
# 
# # Check the result
# V(text_graph_sorted)$start


```

I want to perform this permutation on all documents simultaneously, so I
will write it as a function.

```{r}
permute_start <- function(text_graph) {
  # this function permutes the vertices of a graph by the values of 
  # the attribute "span_start" (specific to my data)
  start_vals <- V(text_graph)$span_start
  sorted_indices <- order(start_vals)
  perm <- match(seq_along(sorted_indices), sorted_indices)
  text_graph_sorted <- permute(text_graph, perm)
  return(text_graph_sorted)
}
```

```{r}
igraphs_nondirected_sorted <- igraphs_nondirected %>% map(permute_start)
write_rds(igraphs_nondirected_sorted, "kuky_data/igraphs_nondirected_sorted.rds")
```

```{r}
igraphs_directed_sorted <- purrr::map2(
  .x = edges_list, 
  .y = vertices_list,
  ~ igraph::graph_from_data_frame(d = .x, vertices = .y, directed = TRUE)) %>% 
  map(permute_start)
write_rds(igraphs_directed_sorted, "kuky_data/igraphs_directed_sorted.rds")
```

