# Network Analysis {#chapter:network_analysis}

In the previous chapter, I prepared a table of edges for the entire ArgM data. In this chapter, I am going to create the input files for a network graph: a table of nodes and a table of edges. 
I will load these into an [`igraph`](https://r.igraph.org/index.html) object and add network characteristics to the nodes to describe their connectedness. 

```{r message=FALSE, warning=FALSE}
library(tidyverse, warn.conflicts = FALSE, quietly = TRUE)
library(igraph, warn.conflicts = FALSE, quietly = TRUE)
library(tokenizers, warn.conflicts = FALSE, quietly = TRUE)
library(magrittr, warn.conflicts = FALSE, quietly = TRUE)
```

 
```{r}

mydata <- read_rds("kuky_data/kuky_argm_total_links.rds")
colnames(mydata)
```

## Vertices (Nodes)

```{r vertices}
vertices_sourcespans <- mydata %>% select(!starts_with("link")) 
vertices_targetspans <- mydata %>% 
  select(doc_id, doc_name, task_type, label = linked_label, 
         start = linked_span_start, end = linked_span_end, 
         span_id = linked_span_id, type, owner, note, plainText, Readability, 
         SyllogismBased, DocumentVersion, ParentDocumentID, LegalActType, 
         Objectivity, Bindingness, AuthorType, RecipientType, 
         RecipientIndividuation, Anonymized, span_text = linked_span_text)

# Check if column names match
if (!identical(colnames(vertices_sourcespans), colnames(vertices_targetspans))) {
stop("Data frames of vertices of source spans and vertices of target spans must have identical column names!")
}
vertices_df <- bind_rows(vertices_sourcespans) %>% relocate(span_id) %>% distinct()
```

### Sanity check
`vertices_df` must contain the same `span_id`s as span_id in `argm.rds`. 

```{r}
argm_spans <- read_rds("kuky_data/argm.rds") %>% pull(span_id)
vertices_spans <- vertices_df %>% pull(span_id)
setdiff(argm_spans, vertices_spans); setdiff(vertices_spans, argm_spans)
rm(argm_spans, vertices_spans)
```
### Get rid of superfluous columns

```{r}
vertices_df %<>% select(!c(task_type, type, note))
```

### Additional span features

- span's relative position in the document 
- span length
- relative span length
- token count in span, neglecting (hopefully most) markup (markdown, html) with a regular expression
- sentence count in span, ditto.

```{r}
vertices_df %<>% group_by(doc_id) %>% 
  mutate(max_end = max(end)) %>% 
  rowwise() %>% 
  mutate(rel_start = round(start/max_end, 2), 
         rel_end = round(end/max_end, 2),
         span_length = (end - start )
         ) %>% 
  mutate(rel_length = round(span_length/max_end, 4)) %>%
  ungroup()    
texts <- vertices_df$span_text %>% 
  str_remove_all("(\\*|#|\\[(\\d|\\.|\\^)+\\]|\\{[^}]+\\}|[\\\\])")  
  words <-  purrr::map_vec(texts, ~ tokenizers::tokenize_words(.x)) %>% 
    map_int(length)
  sentences <-  purrr::map_vec(texts, ~ tokenizers::tokenize_sentences(.x)) %>% 
    map_int(length)
  
  vertices_df %<>% bind_cols("word_count" = words, "sent_count" = sentences)
write_rds(vertices_df, "kuky_data/vertices_df.rds")
write_tsv(vertices_df, "kuky_data/vertices_df.tsv")
```


## Edges
Here I will de-duplicate links that only swap directions. 

```{r}
edges_df <- mydata %>% 
  select(span_id, linked_span_id, link_type, owner) %>% 
  rowwise() %>% 
  mutate(minspan = min(sort(c(span_id, linked_span_id))),
         maxspan = max(sort(c(span_id, linked_span_id))),
         uid = str_c(minspan, maxspan, sep = "---")
         ) %>% 
  ungroup() %>% 
  select(!c(minspan, maxspan)) %>% 
  group_by(uid) %>% arrange(.by_group = TRUE) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(!c(uid))
```
 
Rows before de-duplication: `r nrow(mydata)`.

Rows after de-duplication: `r nrow(edges_df)`. 

## Creating the `igraph` object

The vertex names visible in the graphs are going to be simply the span_ids because the vertices are so many that no 


