# Adding Network-related statistics to the data

## About the input file
In this chapter, I will work with the `igraph` objects of document-owner pairs (some documents were annotated by several annotators in parallel and I treat each as a separate document; hence most documents are uniquely identified with their `doc_id`, but to uniquely identify a document with multiple annotation one needs the  `doc_id` and `doc_owner` combination. I have added a special column called `metadoc_docname_owner`, which is a concatenation of both in the vertices table. The same column was called `doc_owner` in the edges table and remains among the edge attributes).

The `igraph` objects are all stored in a list stored in the RDS files `igraphs` and `igraphs_sorted.rds`. They differ in that the latter has vertices sorted according to their character offset start. This could allow for placing the vertices on a grid in a linear order similar to the span sequence in the linear text. 

The network graphs are non-directed and combine the Stoplight and ArgM annotations. 

## Design issues

The `igraph` library enables me to compute statistics of individual vertices, edges, and whole graphs. I will list the ones I decided to add and say:

1.  to which level of graph they relate (vertex, edge, the entire graph),
2.  what they compute,
3.  and how they could be useful as modeling features.

I am not sure yet whether I will compute everything on the whole graph or on some sub-graphs. I cannot say yet how and when I will have to consider that the logic of the annotation imposes some restrictions on the connectedness of the nodes. The most principal connectedness limitations are: 
- ArgM-to-ArgM edges can only occur between vertices with these combinations of labels: 
  - Law-Narrative
  - Conclusion-Narrative
  - Conclusion-Conclusion
  - Law-Conclusion
  - LegalIssue-Conclusion.
  
- Each ArgM vertex is (or at least should be) connected to at least one Stoplight vertex. 


```{r}
library(tidyverse, warn.conflicts = FALSE, quietly = TRUE)
library(igraph, warn.conflicts = FALSE, quietly = TRUE)
library(magrittr, warn.conflicts = FALSE, quietly = TRUE)

igraphs <- read_rds("kuky_data/igraphs_sorted.rds")

```

I will add the `igraph`-computed statistics directly to the `igraph object` and eventually export all these variables as data frames of vertices and edges. 


I will compute many statistics on three sets of vertices: the complete set of vertices, the subset of vertices that can have edges (henceforth `argum` subset), and the subset of just vertices labeled as Conclusion (henceforth `conclusions` subset). I will use these names throughout the analysis. 
I will create functions to do this subsetting because I will need to make these selections with a purrr function on a list of `igraph` objects. 
I have introduced a `relevance_threshold`, that has a default at 0. If set to larger than 0, vertices that have a smaller value in the `span_Relevant` column are omitted. Their values range from 0 to 1. For more detail about the Stoplight annotation and how it is mapped on the ArgM spans see Section \ref@{section:argm_vertices_stoplight_enriched}. I will compute the statistics on argum and conclusions with different levels of the relevance threshold. In this initial feature extraction, I will use the threshold 0 (relevance neglected) and 0.9 (entirely or almost entirely relevant spans).



```{r}
select_argum_vertices <- function(graph, relevance_threshold = 0) {
  V(graph)[span_label %in% c("Law", "Narrative","Conclusion", 
                                    "LegalIssue") & span_Relevant >= relevance_threshold]
}

select_conclusions_vertices <- function(graph, relevance_threshold = 0){
  V(graph)[span_label == "Conclusion" & span_Relevant >= relevance_threshold]
}
   
```


## Computation of Vertex attributes
```{r}

make_vertex_attr_list <- function(graph){
  list(
    ### Degree ###
    # Normalized for comparison between graphs. Hence I need separate 
    # scenarios for the entire graph, argum with and without relevance threshold, 
    # and conclusions with and without relevance threshold. 
   # vertex_all_degree = degree(graph, loops = FALSE, normalized = TRUE)#,
    vertex_argum_degree_0 = degree(
      subgraph(graph, vids = select_argum_vertices(graph)), loops = FALSE, normalized = TRUE )
    

  # abs_degree = degree(g, loops = FALSE, normalized = FALSE),
  # norm_closeness = closeness(g, normalized = TRUE),
  # norm_betweenness = betweenness(g, normalized = TRUE),
  # abs_betweenness = betweenness(g, normalized = FALSE),
  # transitivity_local = transitivity(g, type = "local", isolates = "NaN"),
  
    #nezapomen na community detection modularity.igraph v Help R a konverzace s MS Copilot
    
  )
}

add_vertex_attr_list <- function(graph) {
  attr_list <- make_vertex_attr_list(graph)

  # Use purrr::iwalk to iterate over the list and set each attribute
  iwalk(attr_list, function(value, name) {
    graph[select_argum_vertices(graph)] <<- set_vertex_attr(graph, name = name, value = value)
  })
  
  return(graph)
}


test <- igraphs[1:2] # a simple igraph object not in a list
test[[1]] %>% make_vertex_attr_list() %>% str()
test <- map(test, ~ add_vertex_attr_list(.x))

test[select_argum_vertices(test)] %>% map( ~ add_vertex_attr_list(.x))


map(test, ~ vertex_attr_names(.x))

```



## Computation of Edge attributes




## Computation of Graph attributes


```{r}
# Named list of vertex attributes
# test <- igraphs[1:2]
# 
# make_vertex_attr_list <- function(graph) {
# attr_list <- list(
#   norm_degree = degree(graph, loops = FALSE, normalized = TRUE),
#   abs_degree = degree(graph, loops = FALSE, normalized = FALSE),
#   norm_closeness = closeness(graph, normalized = TRUE),
#   norm_betweenness = betweenness(graph, normalized = TRUE),
#   abs_betweenness = betweenness(graph, normalized = FALSE),
#   transitivity_local = transitivity(graph, type = "local", isolates = "NaN"),
#   transitivity_global = transitivity(graph, type = "global", isolates = "NaN"))
# return(attr_list)
# }



# Function to create a list of graph-level attributes
make_graph_attr_list <- function(graph) {
  list(
    ### Edge density ###
    graph_edge_density = edge_density(
      graph, 
      loops = FALSE), 
    argum_edge_density_0 = edge_density(
       subgraph(graph, vids = select_argum_vertices(graph)), 
       loops = FALSE), # this considers all argum spans
    argum_edge_density_09 = 
      edge_density( #This considers only argum spans whose 
      # overlap with Stoplight-Relevant is at least 90%. 
      subgraph(graph, vids = select_argum_vertices(graph, 
                                                   relevance_threshold = 0.9))),
      conclusions_edge_density_0 = edge_density(# this considers all Conclusions
      subgraph(graph, vids = select_conclusions_vertices(graph)),
      loops = FALSE),
     conclusions_edge_density_09 = edge_density(# this considers only 
       # Conclusions whose overlap with Stoplight-Relevant is at least 90%.
      subgraph(graph, vids = select_conclusions_vertices(graph, 
      relevance_threshold = 0.9)),
      loops = FALSE),
    ### Edge count ###
    graph_edge_count = ecount(graph), # counts all edges in graph
    argum_edge_count_0 = ecount(  # this considers all argum spans
                           subgraph(graph, vids = select_argum_vertices(graph))),
    argum_edge_count_09 = ecount(subgraph(graph, 
                                            vids = select_conclusions_vertices(
        graph, relevance_threshold = 0.9)) ), # this considers only argum spans 
    #whose overlap with Stoplight-Relevant is at least 90%. 
   conclusions_edge_count_0 = ecount(
     subgraph(graph, vids = select_conclusions_vertices(graph))
     # counts all Conclusions
   ), 
   conclusions_edge_count_09 = ecount(# only Conclusions 90+% relevant
     subgraph(graph, 
              vids = select_conclusions_vertices(graph, 
                                                 relevance_threshold = 0.9))
   ), 
   ### Vertex count ###
   graph_vertex_count = vcount(graph), # counts all vertices in the graph
   argum_vertex_count_0 = vcount( # counts all argum vertices
     subgraph(graph, vids = select_argum_vertices(graph))
   ),
   argum_vertex_count_09 = vcount( # counts only argum vertices 90+% relevant
     subgraph(graph, 
              vids = select_argum_vertices(graph, relevance_threshold = 0.9))
     ), 
   conclusions_vertex_count_0 = vcount( # counts all Conclusions)
      subgraph(graph, vids = select_conclusions_vertices(graph))), 
   conclusions_vertex_count_09 = vcount( # counts only Conclusions 90+% relevant
     subgraph(graph, 
              vids = select_conclusions_vertices(graph, 
                                                 relevance_threshold = 0.9))),
   ### Transitivity (global, weighted) ###
   graph_transitivity_global = transitivity(graph, 
                                            isolates = "zero", #returns 0 if no 
                                            #triangles found in graph
                                              type = "global",
                                            weights = NULL 
                                            # weights default, takes my weights
                                            # attribute in the edges table.
                                            ),
   argum_transitivity_global_0 = transitivity(
     subgraph(graph, vids = select_argum_vertices(graph)),
     isolates = "zero", type = "global", weights = NULL
   ), 
   argum_transitivity_global_09 = transitivity(
     subgraph(graph, vids = select_argum_vertices(graph, 
                                                  relevance_threshold = 0.9)),
     isolates = "zero", type = "global", weights = NULL
   ), 
    conclusions_transitivity_global_0 = transitivity(
     subgraph(graph, vids = select_conclusions_vertices(graph)),
     isolates = "zero", type = "global", weights = NULL
   ), 
   conclusions_transitivity_global_09 = transitivity(
     subgraph(graph, vids = select_conclusions_vertices(graph, 
                                                  relevance_threshold = 0.9)),
     isolates = "zero", type = "global", weights = NULL
   ),
   ### Graph diameter, weighted ###
  graph_diameter_weighted = diameter(graph, directed = FALSE, 
                                       unconnected = TRUE), # returns the largest diameter  
  argum_diameter_weighted_0 = diameter(
    subgraph(graph, vids = select_argum_vertices(graph)), 
    directed = FALSE, unconnected = TRUE
  ) , 
  argum_diameter_weighted_09 = diameter(
    subgraph(graph, vids = select_argum_vertices(graph, 
                                                 relevance_threshold = 0.9)), 
    directed = FALSE, unconnected = TRUE
  ) , 
  conclusions_diameter_weighted_0 = diameter(
        subgraph(graph, vids = select_conclusions_vertices(graph)), 
    directed = FALSE, unconnected = TRUE
  ),
  conclusions_diameter_weighted_09 = diameter(
    subgraph(graph, vids = select_conclusions_vertices(
      graph, relevance_threshold = 0.9)), 
    directed = FALSE, unconnected = TRUE
  ) ,
  conclusions_diameter_unweighted_09 = diameter(
    subgraph(graph, vids = select_conclusions_vertices(
      graph, relevance_threshold = 0.9)), 
    directed = FALSE, unconnected = TRUE, weights = NA
  ) ,
  ### Eigenvector centralization  ###
  # no weights argument available in this function. I have no idea whether it's weighted or not.
  graph_eigenvector_centralization = 
    centr_eigen(graph, directed = FALSE, 
                normalized = TRUE, scale = TRUE)$centralization,
  argum_eigenvector_centralization_0 = 
    centr_eigen(subgraph(graph, vids = select_argum_vertices(graph)), 
                directed = FALSE, normalized = TRUE, scale = TRUE)$centralization,
  argum_eigenvector_centralization_09 = 
    centr_eigen(subgraph(graph, 
                        vids = select_argum_vertices(graph, 
                                                 relevance_threshold = 0.9)), 
                directed = FALSE, normalized = TRUE, scale = TRUE)$centralization,
  conclusions_eigenvector_centralization_0 = 
    centr_eigen(subgraph(graph, vids = select_conclusions_vertices(graph)), 
                directed = FALSE, normalized = TRUE, 
                scale = TRUE)$centralization,
  conclusions_eigenvector_centralization_09 = 
    centr_eigen(
      subgraph(graph, 
              vids = select_conclusions_vertices(graph, 
                                                 relevance_threshold = 0.9)), 
                directed = FALSE, normalized = TRUE, 
      scale = TRUE)$centralization,
  ### Theoretical max of eigenvector centralization
  graph_eigenvector_theoretical_max = centr_eigen(
        graph, scale = TRUE, directed = FALSE, 
        normalized = TRUE)$theoretical_max,
  
  argum_eigenvector_theoretical_max_0 = 
    centr_eigen(subgraph(graph, vids = select_argum_vertices(graph)), 
                directed = FALSE, normalized = TRUE, scale = TRUE)$theoretical_max,
  argum_eigenvector_theoretical_max_09 = 
    centr_eigen(subgraph(graph, 
                        vids = select_argum_vertices(graph, 
                                                 relevance_threshold = 0.9)), 
                directed = FALSE, normalized = TRUE, scale = TRUE)$theoretical_max,
  conclusions_eigenvector_theoretical_max_0 = 
    centr_eigen(subgraph(graph, vids = select_conclusions_vertices(graph)), 
                directed = FALSE, normalized = TRUE, 
                scale = TRUE)$theoretical_max,
  conclusions_eigenvector_theoretical_max_09 = 
    centr_eigen(
      subgraph(graph, 
              vids = select_conclusions_vertices(graph, 
                                                 relevance_threshold = 0.9)), 
                directed = FALSE, normalized = TRUE, 
      scale = TRUE)$theoretical_max#,
  
  # end of list follows with closing parenthesis  
  ) # end of list  
# 
  
   
  
}

# Function to add graph-level attributes to the graph
add_graph_attr_list <- function(graph) {
  attr_list <- make_graph_attr_list(graph)
  
  # Use purrr::iwalk to iterate over the list and set each attribute
  iwalk(attr_list, function(value, name) {
    graph <<- set_graph_attr(graph, name = name, value = value)
  })
  
  return(graph)
}


test <- igraphs[1:2] # a simple igraph object not in a list
test <- map(test, ~ add_graph_attr_list(.x))
map(test, ~ graph_attr(.x))
```



```{r}
## tohle nemazat, to funguje
igraphs %<>% 
  purrr::map2(.y = degrees_all, ~ {V(.x)$degree <- .y
  return(.x)
  })
```

```{r}


# Named list of attributes
attr_list <- list(
  
  
)

# Use purrr::iwalk to assign each attribute
#iwalk(attr_list, function(values, name) {
#  g <<- set_vertex_attr(g, name = name, value = values)
#})
#g
```

```{r}

```













