# Adding Network-related statistics to the data

## About the input file
In this chapter, I will work with the `igraph` objects of document-owner pairs (some documents were annotated by several annotators in parallel and I treat each as a separate document; hence most documents are uniquely identified with their `doc_id`, but to uniquely identify a document with multiple annotation one needs the  `doc_id` and `owner` combination).

The `igraph` objects are all stored in a list stored in the RDS files `igraphs` and `igraphs_sorted.rds`. They differ in that the latter has vertices sorted according to their character offset start. This could allow for placing the vertices on a grid in a linear order similar to the span sequence in the linear text. 

The network graphs are non-directed and combine the stoplight and ArgM annotations. 

## Design issues

The `igraph` library enables me to compute statistics of individual vertices, edges, and whole graphs. I will list the ones I decided to add and say:

1.  to which level of graph they relate (vertex, edge, the entire graph),
2.  what they compute,
3.  and how they could be useful as modeling features.

I am not sure yet whether I will compute everything on the whole graph or on some sub-graphs. I cannot say yet how and when I will have to consider that the logic of the annotation imposes some restrictions on the connectedness of the nodes. The most principal connectedness limitations are: 
- ArgM-to-ArgM edges can only occur between vertices with some combinations of labels: 
  - Law-Narrative
  - Conclusion-Narrative
  - Conclusion-Conclusion
  - Law-Conclusion
  - Legal Issue - Conclusion
  
- each ArgM vertex is (or at least should be) connected to at least one stoplight vertex. 


```{r}
library(tidyverse)
library(igraph)
igraphs <- read_rds("kuky_data/igraphs_sorted.rds")

```

I will create a data frame `graphs_stats_df` to store stats that relate to the entire documents (graphs).

## Edge Density
The proportion of present edges from all possible edges in the network. 

```{r}
gr_density <- purrr::map_vec(igraphs, ~ edge_density(.x)) 
graph_id <- names(gr_density)
graphs_stats_df <- bind_cols("graph_id" = graph_id, "graph_density" = gr_density)
```

## Transitivity

```{r}
gr_transitivity_global <-  purrr::map_vec(igraphs, 
                                          ~ transitivity(.x, 
                                                         type = "global"))
graphs_stats_df %<>% bind_cols(
  "graph_transitivity_global" = gr_transitivity_global)
  
```


## Vertex statistics

```{r}

degrees_all <- purrr::map(igraphs, ~ degree(.x, mode = "all"))

transitivity_local <- purrr::map(igraphs, ~ transitivity(.x, type = "local"))

normalized_closeness <- purrr::map(igraphs, ~ closeness(.x, mode = "all", 
                                                        normalized = TRUE))

```




```{r}
V(igraphs[[1]])$degree <- degrees_all[[1]]
```


```{r}
## tohle nemazat, to funguje
igraphs %<>% 
  purrr::map2(.y = degrees_all, ~ {V(.x)$degree <- .y
  return(.x)
  })
```

```{r}
g <- igraphs[[2]]
library(igraph)
library(purrr)

# Named list of attributes
attr_list <- list(
  norm_degree = degree(g, loops = FALSE, normalized = TRUE),
  abs_degree = degree(g, loops = FALSE, normalized = FALSE),
  norm_closeness = closeness(g, normalized = TRUE),
  norm_betweenness = betweenness(g, normalized = TRUE),
  abs_betweenness = betweenness(g, normalized = FALSE),
  transitivity_local = transitivity(g, type = "local", isolates = "NaN"),
  transitivity_global = transitivity(g, type = "global", isolates = "NaN")
  
)

# Use purrr::iwalk to assign each attribute
iwalk(attr_list, function(values, name) {
  g <<- set_vertex_attr(g, name = name, value = values)
})
g
```

```{r}

```













